
\section{Projects}

%\textbf{BigInteger+Rational, Geometry and Matrices classes} (C++ Programming course, 2020) \link{https://github.com/tkharisov7/object-oriented-programming-mipt}{github link}
%\denseouterlist{
%    \entry {Implemented BigInteger+Rational number class using encapsulation principles of C++. \link{https://github.com/tkharisov7/object-oriented-programming-mipt/tree/main/Biginteger-Rational}{(code)}}
%    \entry {In Geometry used inheritance and polymorphism principles. \link{https://github.com/tkharisov7/object-oriented-programming-mipt/tree/main/Geometry}{(code)}}
%    \entry {Implemented Matrix class with Finite Numbers class including such operations as matrix inversion, matrix determinant computation and so on. \link{https://github.com/tkharisov7/object-oriented-programming-mipt/tree/main/Matrix}{(code)}}
%    \entry {Passed code review and got the excellent mark. (44 points out of 44)}
%}


\begin{comment}
\textbf{BigInteger+Rational, Geometry and Unordered map} (C++ Programming course, 2020-2021) \link{https://github.com/tkharisov7/object-oriented-programming-mipt}{\faicon{github}}
\newline \skill{C++} \skill{Git} \skill{Data Structures} \skill{Unit Testing}
\denseouterlist{
    \entry {Implemented BigInteger+Rational number class using encapsulation principles of C++. \link{https://github.com/tkharisov7/object-oriented-programming-mipt/tree/main/Biginteger-Rational}{(code)}}
    \entry {Geometry class provides such features as user-determined polygons, ellipses and others. Also it has helpful functions to compute various characteristics of shapes like area, triangle circumcenter and so on. Implementation uses inheritance and polymorphism principles. \link{https://github.com/tkharisov7/object-oriented-programming-mipt/tree/main/Geometry}{(code)}}
    \entry {Implemented STL-like unordered map class. It uses my own list with custom allocators to improve the overall performance \textbf{more than twice} comparing to the standard library unordered map. Also class is template based and uses such features as allocator traits to make it user-defined. \link{https://github.com/tkharisov7/Algo-2-sem/tree/main/unordered_map}{(code)}}
    \entry {Passed code review and got the excellent mark. \emph{(44 points out of 44)}}
}
\end{comment}

\begin{comment} 
\textbf{BigInteger+Rational, Geometry and Unordered map} (C++ Programming course, 2020-2021) \link{https://github.com/tkharisov7/object-oriented-programming-mipt}{\faicon{github}}
\newline \skill{C++} \skill{Git} \skill{Data Structures} \skill{Unit Testing}
\denseouterlist{
    \entry {Implemented template based STL-like unordered map class. It uses my own list with custom allocators to improve the overall performance \textbf{more than twice} comparing to the standard library unordered map. Passed code review and got the excellent mark. \emph{(44 points out of 44)} \link{https://github.com/tkharisov7/Algo-2-sem/tree/main/unordered_map}{(code)}}
}
\end{comment}
%\begin{comment}
\textbf{C++ console game inspired by Reigns game.} (Industrial Programming course, 2021) \link{https://github.com/tkharisov7/console-game}{\faicon{github}}
\newline \skill{C++} \skill{CMake} \skill{Git} \skill{Software Design Patterns} 
\denseouterlist{
    \entry {Collaborated with a friend of mine and wrote a fully playable console quest game. Project was reviewed by teaching assistant and got \emph{30 points out of 30}, ranking \textbf{top 1 of 80 among all coursemates}.}
}
%\end{comment}

\begin{comment}
\textbf{Web application for tracking goals} (Personal project, 2021) \link{https://github.com/tkharisov7/To-Do-Web-App}{\faicon{github}}
\newline \skill{Python} \skill{Flask} \skill{SQL} \skill{Bootstrap} \skill{Git}
\denseouterlist{
    \entry{Developed a Python web application that helps to track personal goals. It has useful features to help complete routine tasks. (The Frog Method feature)}
}
\end{comment}

\textbf{Automatic Essay Scoring for IELTS Writing} (Personal Project, 2023)\link{https://github.com/tkharisov7/AES-IELTS}{\faicon{github}}
\newline \skill{Transformers} \skill{NLP} \skill{Python} 
\denseouterlist{
    \entry{ Developed a BERT-based model to predict the overall scores for IELTS Academic Part 2 tasks. It accurately forecasts scores within the high band range.}
}